\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}

\title{Test Document 4: Citations and References}
\author{Bibliography Test}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This document demonstrates bibliography and citation handling in LaTeX.
\end{abstract}

\section{Introduction}
Scientific writing requires proper citations. According to Smith et al. \cite{smith2020}, proper referencing is crucial for academic integrity. This was further confirmed by Johnson \cite{johnson2021}.

\section{Literature Review}
The field has evolved significantly over the years \cite{brown2019, davis2020}. Multiple studies have shown the importance of this topic \cite{wilson2018, taylor2022}.

\subsection{Recent Developments}
As noted in \cite{anderson2023}, recent advances have changed our understanding. The comprehensive review by \cite{thompson2022} provides an excellent overview.

\section{Methodology}
Following the approach described in \cite{martinez2021}, we implemented the standard protocol.

\section{Conclusion}
This work builds upon the foundation laid by \cite{garcia2020} and extends the findings of \cite{rodriguez2019}.

\begin{thebibliography}{99}

\bibitem{smith2020}
Smith, J., Doe, A., and Brown, K.,
\textit{Fundamentals of Academic Writing},
Journal of Education, vol. 45, pp. 123-145, 2020.

\bibitem{johnson2021}
Johnson, L.,
\textit{Citation Practices in Modern Academia},
Academic Press, 2021.

\bibitem{brown2019}
Brown, M. and Green, S.,
\textit{Evolution of Scientific Writing},
Science Communications, vol. 12, no. 3, pp. 67-89, 2019.

\bibitem{davis2020}
Davis, R.,
\textit{The Importance of Proper References},
Research Methods Quarterly, vol. 8, pp. 234-250, 2020.

\bibitem{wilson2018}
Wilson, P.,
\textit{Academic Integrity Guidelines},
University Publishing, 2018.

\bibitem{taylor2022}
Taylor, H. and White, J.,
\textit{Modern Citation Standards},
Educational Review, vol. 56, pp. 445-467, 2022.

\bibitem{anderson2023}
Anderson, C.,
\textit{Recent Advances in Documentation},
Tech Writing Journal, vol. 15, no. 1, pp. 12-28, 2023.

\bibitem{thompson2022}
Thompson, E.,
\textit{Comprehensive Review of Citation Methods},
Annual Review of Information Science, vol. 77, pp. 89-112, 2022.

\bibitem{martinez2021}
Martinez, D. and Lopez, F.,
\textit{Standard Protocols for Research Documentation},
Methodology International, vol. 34, pp. 567-589, 2021.

\bibitem{garcia2020}
Garcia, M.,
\textit{Foundations of Scientific Documentation},
Academic Publishers, 2020.

\bibitem{rodriguez2019}
Rodriguez, A.,
\textit{Extended Analysis of Reference Systems},
Journal of Documentation, vol. 41, no. 4, pp. 789-812, 2019.

\end{thebibliography}

\end{document}